Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Update comment

    BDD is meant to be an enjoyable experience for the developer.  It
    provides compared to TDD it provides a much nicer syntax that
    makes tests very easy to read.  And like TDD it puts emphasis on
    test automation, to take load from the shoulders of developers.
\end{quote}

>>>>

    BDD is meant to be an enjoyable experience for the developer.
    Compared to TDD it provides a much nicer syntax that
    makes tests very easy to read.  And like TDD it puts emphasis on
    test automation, to take work load from the shoulders of
    developers.
\end{quote}
